---
title: "Sex-Biased Dispersal in the Sonoran Desert Bark Beetle"
author: "Renée Hilelson & <a href='http://dyerlab.org'>Rodney Dyer</a>"
date: "<a href='https://ces.vcu.edu'>Center for Environmental Studies</a></br><a href='https://vcu.edu'>Virginia Commonwealth University</a></br>Richmond Virginia 23284"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, 
                      message = FALSE, 
                      warning = FALSE)
library( tidyverse )
```


> This is where the abstract goes... Blah blah blah.



## Introduction







## Methods




```{r }
data <- read_csv("data/Araptus_Samples.csv")
summary(data)
```

We sampled *N = `r nrow(data)`* locales.  At each site, we sampled 10 plants within a 1 km area.  On each plant, we collected all beetles for subsequent sex determination in the lab.


We defined sex ratio as ...
```{r}
# data$SexRatio <- 
```


## Results

The observed sex census counts of male ranged from `r min(data$Males)` - `r max(data$Males)` and females from `r min(data$Females)` - `r max(data$Females)`.

Sex ratio varied from xxx  to xxx for the sites

## Discussion



## Acknowledgements



## Tables 


```{r}
library(raster)
library(leaflet)

raster( "data/alt_22.tif" ) %>%
  crop( extent( -116, -108, 22, 30 ) ) %>%
  rasterToPoints() %>% 
  data.frame() -> elevation
summary(elevation)
ggplot( elevation, aes(x,y,fill=alt_22)) + geom_raster() 
```

Table 1: make a table  with `SAMPLE SITES, LATITUDE, LoNGITUDE, ELEVATION`
```{r}
library( sp )
pts <- SpatialPoints( cbind( data$Longitude, data$Latitude)  )
class( pts )


elev <- raster( "data/alt_22.tif" )
data$Elevation <- extract( elev, pts )

library( tidyverse )
data %>%
  dplyr::select( Site, Longitude, Latitude, Elevation ) %>%
  knitr::kable() %>%
  kableExtra::kable_styling()
```


## Figures

Figure 1: Map of study locations
```{r}
data %>%
  leaflet()%>%
  addTiles() %>%
  addMarkers( ~Longitude, ~Latitude, label = ~Suitability)

  
```


Figure 2: Sex Ratio ~ Latitude

```{r}
library(ggplot2)
library(ggrepel)

data %>%
  ggplot(aes(Latitude, MFRatio)) +
  xlab("Sex Ratio") +
  geom_point()+
  stat_smooth()
```


Figure X: Habitat Suitability
```{r}
data %>%
  ggplot(aes(Suitability, 1.0/MFRatio)) +
  geom_point()+
    stat_smooth()
```

Figure 3: Sex Ratio ~ Habitat Suitability

## Citations





